### 2023-02-17 source/paper3.tex
typos

\node (PRS) [below = 4.5em of rData]
{\begin{tabular}{c} \textbf{Probability of replication success} \\
   {\scriptsize $\Pr(X_r \in S \given n_{r}, x_{o}, \mathrm{external
    knowledge})$}
 \end{tabular}};

@@

There are some limitations and possible extensions: we have developed the
methodology for ``direct'' replication studies \citep{Simons2014} which attempt
to replicate the conditions from the original study as closely as possible; yet
SSD methodology is also needed for ``conceptual'' replication and for
``generalization'' studies which may show systematic deviations from the
original study. While the heterogeneity variance in the design prior allows to
take effect size heterogeneity into account for SSD, to some extent, further
research is needed for investigating how systematic study deviations and
external knowledge can be incorporated. Furthermore, as is standard in
meta-analysis we assumed that the variances of the effect estimates are known,
which can sometimes be inadequate \citep{Jackson2018}. Specifying priors also
for the variances could better reflect the available uncertainty but would come
at the price of lower interpretability and higher computational complexity. We
did also not consider designs where the replication data are analyzed in a
sequential manner. Ideas from the Bayesian sequential design
\citep{Schoenbrodt2017, Stefan2022} or from the adaptive trials literature
\citep{Bretz2009} could be adapted to the replication setting as in
\citet{Micheloud2020}. A sequential analysis of the replication data could
possibly increase the efficiency of the replication. An additional point is that
we assumed that the original study has been completed when planning the
replication study. One could also consider a scenario where both the original
and replication study are planned simultaneously and adopt a ``project''
perspective \citep{Maca2002, Held2021}. However, in this case no information from
the original study is available and the design prior needs to be specified
entirely based on external knowledge. Finally, researchers have only limited
resources and it may happen that they cannot afford a large enough sample size
to obtain their desired probability of replication success. In this situation a
reverse-Bayes approach \citep{Held2021b} could be applied in order to determine
the prior for the effect size which is required to achieve the desired
probability of replication success based on the maximally possible sample size.
Researchers can then judge whether or not such prior beliefs are scientifically
sensible, and decide whether they should conduct the replication study with
their limited resources.

>>>>

\node (PRS) [below = 4.5em of rData]
{\begin{tabular}{c} \textbf{Probability of replication success} \\
   {\scriptsize $\Pr(X_r \in S \given n_{r}, x_{o}, \mathrm{external~
    knowledge})$}
 \end{tabular}};

@@

There are some limitations and possible extensions: we have developed the
methodology for ``direct'' replication studies \citep{Simons2014} which attempt
to replicate the conditions from the original study as closely as possible; yet
SSD methodology is also needed for ``conceptual'' replication and for
``generalization'' studies which may show systematic deviations from the
original study. While the heterogeneity variance in the design prior allows to
take effect size heterogeneity into account for SSD, to some extent, further
research is needed for investigating how systematic study deviations and
external knowledge can be incorporated. Furthermore, as in standard in
meta-analysis we assumed that the variances of the effect estimates are known,
which can sometimes be inadequate \citep{Jackson2018}. Specifying priors also
for the variances could better reflect the available uncertainty but would come
at the price of lower interpretability and higher computational complexity. We
did also not consider designs where the replication data are analyzed in a
sequential manner. Ideas from the Bayesian sequential design
\citep{Schoenbrodt2017, Stefan2022} or from the adaptive trials literature
\citep{Bretz2009} could be adapted to the replication setting as in
\citet{Micheloud2020}. A sequential analysis of the replication data could
possibly increase the efficiency of the replication. An additional point is that
we assumed that the original study has been completed when planning the
replication study. One could also consider a scenario where both the original
and replication study are planned simultaneously and adopt a ``project''
perspective \citep{Maca2002, Held2021}. However, in this case no information from
the original study is available and the design prior needs to be specified
entirely based on external knowledge. Finally, researchers have only limited
resources and it may happen that they cannot afford a large enough sample size
to obtain their desired probability of replication success. In this situation a
reverse-Bayes approach \citep{Held2021b} could be applied in order to determine
the prior for the effect size which is required to achieve the desired
probability of replication success based on the maximally possible sample size.
Researchers can then judge whether or not such prior beliefs are scientifically
sensible, and decide whether they should conduct the replication study with
their limited resources.

### 2023-02-17 source/paper4.tex
polish
typos

It is straightforward to extend \eqref{eq4:eq0} and \eqref{eq4:eq1} to hypotheses
that involve unknown parameters $\theta$. The likelihood ratio
$\Pr(\data \given H_{1})/\Pr(\data \given H_{0})$ is then called a Bayes factor
\citep{Jeffreys1961, Kass1995} where
\begin{equation*}
  \Pr(\data \given H_{i}) = \int \Pr(\data \given \theta, H_{i}) \p(\theta \given H_{i}) d
  \theta
\end{equation*}
is the marginal likelihood under hypothesis $H_i$, $i=0,1$, obtained be
integration of the ordinary likelihood with respect to the prior distribution
$\p(\theta \given H_i)$. We will apply the Reverse-Bayes approach to Bayes
factors in Section \ref{sec4:bfs} and \ref{sec4:p.equals}.

@@

\section{Bayes factor for intrinsic credibility}
\label{app:BFIC}
Intrinsic credibility at level $\gamma$ is established when
\begin{align}
  \label{eq4:ic-condition}
  \BF_{12} \leq \BF_{01} = \gamma
\end{align}
and we are interested in the Bayes factor for intrinsic credibility $\BFIC$
which is the smallest level $\gamma \in (0, 1]$ where~\eqref{eq4:ic-condition}
holds. The $\BFIC$ is therefore a special case of the sceptical Bayes factor
from \citet{Pawel2020b} where the same data is used in both Bayes factors
(instead of the data from a replication study for $\BF_{12}$). It is hence given
by
\begin{align}
  \label{eq4:BFic}
  \BFIC =
  \begin{cases}
    \sqrt{-z^{2}/k}\cdot \exp\left\{-(z^{2} + k)/2\right\}
    & \text{if} \abs{z} \geq \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\}\\
    \mbox{minBF}_{01} \
    & \text{if} ~ \sqrt{\log 2} \leq \abs{z} < \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\} \\
    \text{undefined}
    & \text{if} ~ \abs{z} < \sqrt{\log 2}
  \end{cases}
\end{align}
with $k = \mathrm{W}(-z^{2} \exp\{-z^{2}/2\}/\sqrt{2})$ and $\mathrm{W}(\cdot)$
the branch of the Lambert W function that satisfies $\mathrm{W}(y) \leq -1$ for
$y \in [-e^{-1}, 0).$ If
$\abs{z} \geq \sqrt{-2 W(-e^{-1}/\sqrt2)} \approx 2.04$, $\BFIC$ is located at
the intersection between $\BF_{12}$ and $\BF_{01}$ in the relative prior
variance $g$, so equation (7) from \citet{Pawel2020b} can be used. For
$\abs{z} \geq \sqrt{\log 2} \approx 0.83$, $\BF_{12}$ remains below $\BF_{01}$
for all $g$ and hence $\BFIC$ is given by $\mbox{minBF}_{01}$, the minimum of
$\BF_{01}$ from \eqref{eq4:minBFnorm}. Finally, when $\abs{z} < \sqrt{\log 2}$,
equation~\eqref{eq4:ic-condition} cannot be satisfied for any valid sufficiently
sceptical relative prior variance $g$, hence the $\BFIC$ is undefined.

>>>>

It is straightforward to extend \eqref{eq4:eq0} and \eqref{eq4:eq1} to hypotheses
that involve unknown parameters $\theta$. The likelihood ratio
$\Pr(\data \given H_{1})/\Pr(\data \given H_{0})$ is then called a Bayes factor
\citep{Jeffreys1961, Kass1995} where
\begin{equation*}
  \Pr(\data \given H_{i}) = \int \Pr(\data \given \theta, H_{i})\,
  \p(\theta \given H_{i}) \,\mathrm{d} \theta
\end{equation*}
is the marginal likelihood under hypothesis $H_i$, $i=0,1$, obtained be
integration of the ordinary likelihood with respect to the prior distribution
$\p(\theta \given H_i)$. We will apply the Reverse-Bayes approach to Bayes
factors in Section \ref{sec4:bfs} and \ref{sec4:p.equals}.

@@

\section{Bayes factor for intrinsic credibility}
\label{app:BFIC}
Intrinsic credibility at level $\gamma$ is established when
\begin{align}
  \label{eq4:ic-condition}
  \BF_{12} \leq \BF_{01} = \gamma
\end{align}
and we are interested in the Bayes factor for intrinsic credibility $\BFIC$
which is the smallest level $\gamma \in (0, 1]$ where~\eqref{eq4:ic-condition}
holds. The $\BFIC$ is therefore a special case of the sceptical Bayes factor
from \citet{Pawel2020b} where the same data is used in both Bayes factors
(instead of the data from a replication study for $\BF_{12}$). It is hence given
by
\begin{align}
  \label{eq4:BFic}
  \BFIC =
  \begin{cases}
    \sqrt{-z^{2}/k}\cdot \exp\left\{-(z^{2} + k)/2\right\}
    & \text{if} \abs{z} \geq \surd\big\{-2 \mathrm{W}\big(-e^{-1}/\sqrt2\big)\big\}\\
    \mbox{minBF}_{01} \
    & \text{if} ~ \sqrt{\log 2} \leq \abs{z} < \surd\big\{-2 \mathrm{W}\big(-e^{-1}/\sqrt2\big)\big\} \\
    \text{undefined}
    & \text{if} ~ \abs{z} < \sqrt{\log 2}
  \end{cases}
\end{align}
with $k = \mathrm{W}(-z^{2} \exp\{-z^{2}/2\}/\sqrt{2})$ and $\mathrm{W}(\cdot)$
the branch of the Lambert W function that satisfies $\mathrm{W}(y) \leq -1$ for
$y \in [-e^{-1}, 0).$ If
$\abs{z} \geq \sqrt{-2 \mathrm{W}(-e^{-1}/\sqrt2)} \approx 2.04$, $\BFIC$ is
located at the intersection between $\BF_{12}$ and $\BF_{01}$ in the relative
prior variance $g$, so equation (7) from \citet{Pawel2020b} can be used. For
$\abs{z} \geq \sqrt{\log 2} \approx 0.83$, $\BF_{12}$ remains below $\BF_{01}$
for all $g$ and hence $\BFIC$ is given by $\mbox{minBF}_{01}$, the minimum of
$\BF_{01}$ from \eqref{eq4:minBFnorm}. Finally, when $\abs{z} < \sqrt{\log 2}$,
equation~\eqref{eq4:ic-condition} cannot be satisfied for any valid sufficiently
sceptical relative prior variance $g$, hence the $\BFIC$ is undefined.

### 2023-02-17 source/paper6.tex
typos

The penalized log-likelihood for \ainet{} for a single observation $(\ry, \rx)$
is defined as
$$\ell_{\text{AINET}}(\beta_0, \shiftparm; \ry, \rx, \alpha, \lambda, \wvec) =
  \ell(\beta_0, \shiftparm; \ry, \rx) + \aipen$$
where
$$\ell(\beta_0, \shiftparm; \ry, \rx) =
\ry \log\left(\expit\left\{\beta_0 + \linpred\right\}\right) + (1 - \ry) \log\left(1 - \expit\left\{\beta_0 + \linpred\right\}\right)$$
denotes the log-likelihood of a binomial GLM and $\wvec$ is derived from a
random forest variable importance measure $\widetile{IMP}$ as
$$w_j = 1 - \left(\frac{\IMP_j}{\sum_{k=1}^p \IMP_k}\right)^\gamma,$$
where we transform $\IMP$ to be non-negative via
$$\IMP_j = \max\{0, \widetilde\IMP_j\}$$
and $\gamma$ is a hyperparameter for the influence of the weights similar to
$\gamma$ hyperparameter of the adaptive elastic net. \ainet{} is fitted by
maximizing its penalized log-likelihood assuming i.i.d. observations
$\{(\ry_i, \rx_i)\}_{i=1}^n$, \ie
$$\arg\max_{\beta_0, \shiftparm} \sum_{i = 1}^n \ell_{\text{AINET}}(\beta_0,
\shiftparm; \ry_i, \rx_i, \alpha, \lambda, \wvec).$$

>>>>

The penalized log-likelihood for \ainet{} for a single observation $(\ry, \rx)$
is defined as
$$\ell_{\text{AINET}}(\beta_0, \shiftparm; \ry, \rx, \alpha, \lambda, \wvec) =
  \ell(\beta_0, \shiftparm; \ry, \rx) + \aipen$$
where
$$\ell(\beta_0, \shiftparm; \ry, \rx) =
\ry \log\left(\expit\left\{\beta_0 + \linpred\right\}\right) + (1 - \ry) \log\left(1 - \expit\left\{\beta_0 + \linpred\right\}\right)$$
denotes the log-likelihood of a binomial GLM and $\wvec$ is derived from a
random forest variable importance measure $\widetilde{\IMP}$ as
$$w_j = 1 - \left(\frac{\IMP_j}{\sum_{k=1}^p \IMP_k}\right)^\gamma,$$
where we transform $\IMP$ to be non-negative via
$$\IMP_j = \max\{0, \widetilde\IMP_j\}$$
and $\gamma$ is a hyperparameter for the influence of the weights similar to
$\gamma$ hyperparameter of the adaptive elastic net. \ainet{} is fitted by
maximizing its penalized log-likelihood assuming i.i.d. observations
$\{(\ry_i, \rx_i)\}_{i=1}^n$, \ie
$$\arg\max_{\beta_0, \shiftparm} \sum_{i = 1}^n \ell_{\text{AINET}}(\beta_0,
\shiftparm; \ry_i, \rx_i, \alpha, \lambda, \wvec).$$
